Causal Assumptions - DAG

### 2023-10-18 analysis/dag.qmd
got a model!

# set theme of all DAGs to `theme_dag()`
theme_set(theme_dag(base_family = "Cantarell"))

@@

## Specify a Causal Question

@@

## Exploratory Data Analysis

```{r eda, warning=FALSE, message=FALSE}
#| fig-width: 10

data <- read_csv(here("data", "all.csv"))

data |>
  filter(ich_location == c("Lobar", "Basal Ganglia", "Thalamus")) |>
  filter(!is.na(ich_laterality)) |>
  ggplot(aes(euro_vas_90, fill = ich_laterality)) +
  geom_density(color = NA, alpha = .8)

@@

```{r}

>>>>

# set theme of all DAGs to `theme_dag()`
theme_set(theme_dag(base_family = "Noah"))

@@

## Specify Causal Questions

Do patients with **left hemispheric** injuries receive less aggressive care as compared to patients with **right hemispheric** injuries? We will look at rates of neurosurgery, evd, tracheostomy, withdrawal of life-sustaining therapies.

@@

@@
